Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-08-24 ms_pre_post.Rmd
Add Polyandry section to the Model

```{r,echo=FALSE}
#**First paragraph** A general overview of what the model is doing, which will look a lot like Duthie and Reid (AmNat) and Duthie et al. (Evolution). Mention somewhere in here that all individuals have 30 diploid loci, ten with alleles affecting polyandry, ten with alleles affecting pre-copulatory inbreeding strategy, and ten with alleles affecting post-copulatory inbreeding strategy. Also note that the traits affected by each of these loci can each potentially come with some cost ($c_P$, $c_M$, and $c_F$). Note that we are not assuming any constraints on accessibility to males, so all males are available at all times.
```

We track interactions among discrete individuals in a small focal population that persists over multiple generations. Individuals within this population are either female or male, and are potentially related if they share a common ancestory. We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent, between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie]. At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding. The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$). A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates. Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$. After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults. After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity. Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.

@@

>>>>

We track interactions among discrete individuals in a small focal population that persists over multiple generations. Individuals within this population are either female or male, and are potentially related if they share a common ancestory. We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent [@Lynch1998], between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie]. At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding. The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$). A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates. Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$. After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults. After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity. Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.

@@

Each female chooses a number of males to mate with ($N_{males}$) based on her genetically determined tendency to engage in polyandry ($P_{p}$). The exact value of $N_{males}$ is calculated by sampling from a random poisson distribution such that $N_{males} = Poisson(P_{p}) + 1$. This random sampling procedure causes some stochastic variation in the number of realised mates a that female chooses, with a mean $N_{males}$ of $P_{p}+1$. A one is added to $P_{p}$ to ensure that all females choose at least one mate, as low values of $P_{p}$ might return $Poisson(P_{p})$ values of zero.

The value of $P_{p}$ is affected by the summed values of her 20 $P_{a}$ alleles. Inheritence of all alleles models a diploid genetic architecture in which 10 $P_{a}$ alleles are randomly sampled from each parent with no physical linkage. Values of $P_{a}$ can take any real number [continuum-of-alleles model; @Kimura1965; @Lande1976; @Reeve2000; @Bocedi2014]. The tendency for polyandry genotype $P_{g}$ is defined by the sum of all of a focal female's 20 $P_{a}$ values, which might be negative or positive. However, the tendency for polyandry phenotype $P_{p}$ is restricted to zero or positive values because the number of males that a female chooses to mate with cannot be negative. Hence, negative values of $P_{g}$ are translated to $P_{p}$ values of zero such that $P_{p} = 0$ when $P_{g} < 0$, but when $P_{g} \geq 0$, then $P_{p} = P_{g}$ (i.e., the phenotype value of polyandry equals the genotype value of polyandry if and only if the genotype value is greater than or equal to zero, else the phenotype value of polyandry always equals zero). The resulting $P_{p}$ is therefore modelled as a threshold trait [@Lynch1998; @Roff1996; @Roff1998], in which polyandry is expressed discretely at the threshold value of $P_{g} > 0$, but is determined by the consequence of continuous genetic variation arising from the effects of $P_{a}$ alleles that each contribute additively to a female's tendency toward polyandry. Negative genotypic values of $P_{g}$ therefore all have the same phenotype, resulting in consistently monandrous females. In contrast, positive values of $P_{g}$ and therefore $P_{p}$ can lead to different degrees of realised polyandry in the form of discrete numbers of mates ($N_{males}$).

Mating
----------------------------------------------
